The Castro AMR Simulation Code: Current and Future Developments

### 2020-02-03 astronum_2019_Castro/astronum-castro-2019.tex
update ref response

\castro\ implements both a second-order method (using a trapezoid rule
for the integral) and fourth-order method in space and time (using a
Simpsons rule for the integral and the spatial reconstruction of
\cite{mccorquodalecolella}).  We demonstrated that \castro\ achieves
the expected convergence on a wide variety of problems in
\cite{castro:sdc}.  Table~\ref{table:convergence} summaries the
convergence of the standard unsplit CTU PPM hydrodynamics algorithm
with Strang splitting and the second- and fourth-order SDC methods on
a reacting acoustic pulse test problem.

@@

>>>>

\castro\ implements both a second-order method (using a trapezoid rule
for the integral) and fourth-order method in space and time (using a
Simpsons rule for the integral and the spatial reconstruction of
\cite{mccorquodalecolella}).  We demonstrated that \castro\ achieves
the expected convergence on a wide variety of problems in
\cite{castro:sdc}.  Table~\ref{table:convergence} summaries the
convergence of the standard unsplit CTU PPM hydrodynamics algorithm
with Strang splitting and the second- and fourth-order SDC methods on
a reacting acoustic pulse test problem modeling the 3-$\alpha$ and
$\isotm{C}{12}(\alpha,\gamma)\isotm{O}{16}$ reactions.  We see that
the Strang CTU method has trouble achieving second order accuracy,
while the second-order SDC method converges second order.  The
fourth-order SDC method converges almost fourth order overall.  Full
details of this problem and more extensive convergence results are
given in \cite{castro:sdc}.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{flame_wave_smallplt131070_slice}
\caption{\label{fig:xrb} A snapshot of a 20 cm XRB flame calculation showing
the mean molecular weight.  The flame is moving from left to right, and we see
a gradient in the ash behind the flame, as the burning makes heavier nuclei.  
Calculation from \cite{eiden:2019}.}
\end{figure}
